quollr: An R Package for Visualizing $2-D$ Models from Non-linear Dimension Reductions in High Dimensional Space

### 2024-06-22 paper-quollr.Rmd
Update the main function

The following demonstration of the package's functionality assumes `quollr` has been loaded. We also want to load the built-in data sets `s_curve_noise_training`, `s_curve_noise_test` and `s_curve_noise_umap`.

`s_curve_noise_training` is a $3-D$ S-curve dataset with additional four noise dimensions which is used to train the model. `s_curve_noise_test` is used for prediction. `s_curve_noise_umap` is the UMAP $2-D$ embedding for `s_curve_noise_training` dataset. Each dataset contains a unique ID column.

@@

@@

The mains steps for the algorithm can be executed by the main function `fit_highd_model()`, or can be run separately for more flexibility. When constructing the 2D model, the user can choose either to fit the 2D model with hexagonal bin centroids or bin means using `is_bin_centroid` argument.

@@

The number of bins along the x axis, the ratio of the ranges of the original embedding components, and if `is_rm_lwd_hex = TRUE`, benchmark value to remove low density hexagons are parameters that will be determined within `fit_highd_model`, if they are not provided. They are created as they are needed throughout the following example.

```{r, echo=TRUE}
fit_highd_model(
  training_data = s_curve_noise_training,
  emb_df = s_curve_noise_umap_scaled, 
  bin1 = 15, r2 = r2, 
  is_bin_centroid = TRUE,
  is_rm_lwd_hex = TRUE,
  benchmark_to_rm_lwd_hex = NULL,
  col_start_highd = "x"
  )
```

>>>>

The following demonstration of the package's functionality assumes `quollr` has been loaded. We also want to load the built-in data sets `s_curve_noise_training` and `s_curve_noise_umap`.

`s_curve_noise_training` is a $3\text{-}D$ S-curve data set with additional four noise dimensions which is used to train the model. `s_curve_noise_umap` is the UMAP $2\text{-}D$ embedding for `s_curve_noise_training` data set. Each data set contains a unique ID column.

@@

The algorithm begins by scaling NLDR data to a standard scale using the `gen_scaled_data()` function. This function standardizes the data and provides the original limits of embeddings and the aspect ratio.

@@

The mains steps for the algorithm can be executed by the main function `fit_highd_model()`, or can be run separately for more flexibility. When constructing the $2\text{-}D$ model, the user can choose either to fit the $2\text{-}D$ model with hexagonal bin centroids or bin means using `is_bin_centroid` argument.

@@

The number of bins along the x-axis, the ratio of the ranges of the original embedding components, the buffer amount as a proportion of data, and if `is_rm_lwd_hex = TRUE`, benchmark value to remove low density hexagons are parameters that will be determined within `fit_highd_model`, if they are not provided. They are created as they are needed throughout the following example.

```{r, echo=TRUE}
fit_highd_model(
  training_data = s_curve_noise_training,
  emb_df = s_curve_noise_umap_scaled, 
  bin1 = 12, 
  r2 = r2,
  q = 0.07,
  is_bin_centroid = TRUE,
  is_rm_lwd_hex = TRUE,
  benchmark_to_rm_lwd_hex = NULL,
  col_start_highd = "x"
  )
```
